Challenge 1: Energy Production Data Simulation
========================================================

Preparation
--------------------------------------------------------
Load libraries:
```{r}
require(ggplot2, quiet = TRUE)
require(lubridate, quiet = TRUE)
```

Load data:
```{r}
training <- read.csv("../../data/training_dataset_500.csv")
```

Exploration
--------------------------------------------------------
First, let's see what we're dealing with:
```{r}
summary(training)
head(training)
```

```{r}
training$startdate <- ymd(paste(training$Year, training$Month, 1))
training$House <- factor(training$House)
```

And check for missing data:
```{r}
ggplot(training) + geom_tile(aes(x = startdate, y = House, colour = EnergyProduction))
```
Doesn't look like we have missing data, but there appears to be a periodicity in the houses. If the labels are arbitrary, this shouldn't happen. Hopefully its just due to them having been sorted somehow before naming.

Let's look at some kernel density estimates:
```{r}
densityplot <- ggplot(training) + geom_density()
densityplot + aes(x = Temperature)
densityplot + aes(Daylight)
densityplot + aes(EnergyProduction)

```

Now let's look at the correlations between `Temperature`, `Daylight` and `EnergyProduction`. I'm not sure exactly what `Daylight` measures, but I'd guess that it's correlated with `Temperature`. I also expect `EnergyProduction` to have some correlation with both.
```{r}
cor(training[,c('Temperature', 'Daylight', 'EnergyProduction')])
```
`EnergyProduction` has the expected correlations, but the very low correlation between `Temperature` and `Daylight` is pretty surprising. One or both of these may not mean what I think it means. 

Prediction
-------------------------------------------------------
The first thing to do before modelling a system is to make sure you understand it, in particular the causes and effects. 
Let's first make some assumptions about the dataset:
- The `EnergyProduction` column describes the total energy produced by an array of solar panels, over a given month.
- `Daylight` could mean a number of different things. With a maximum of 271, it is too small to be hours of sunlight in the month. It has decimal points and +ve correlation with `EnergyProduction` so it can't be based on Oktas.
- Temperature is the average temperature in the month. Or is it? If this is British data, in Celsius, then 0.8 seems too low, and 29 too high.

# todo
-continue discussion of the model.
-maybe look at correlations with number of days in the month

